\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{array}
\usepackage{enumitem}

\title{Math for Computer Science - In class Problems - Week 3}
\author{Fredy Ranthun}
\date{\today}

\begin{document}

\maketitle

\section*{Problem 1}

\section*{Problem 2}
\begin{enumerate}[label=\alph*.]
  \setlength{\itemindent}{0pt}
  \item \[
          \exists u (uuu = x)
        \]
        Name: THREE-COPIES($x$)
  \item \[
          \exists u (uu = x \text{ AND } \text{NO-1S}(u))
        \]
        Name: EVEN-LENGTH-AND-NO-1S($x$)
  \item \[
          \text{NOT}(\text{SUBSTRING}(1,x)) \text{ OR } \text{NOT}(\text{SUBSTRING}(0,x))
        \]
        Name: ONLY-0S-OR-ONLY-1S($x$)
  \item \[
          \exists u (1u1 = x \text{ AND } \text{NO-1S}(u))
        \]
        Name: IS-2k+1($x$)
  \item Let's assume x contains at least a 1. This way x will not be the prefix of '0x',
        since each 1 would shifted to the right.
\end{enumerate}

\section*{Problem 3}

\[
  \exists s \forall t_1 \forall t_2 \forall t_3 \left(E(s, t_1) \land E(s, t_2) \implies t_1 = t_2 \lor t_1 = t_3 \lor t_2 = t_3 \right)
\]

\section*{Problem 4}

\section*{Problem 5}
\begin{enumerate}[label=\alph*.]
  \setlength{\itemindent}{0pt}
  \item There are at least three different people, x, y and z which belongs to the cabal.
  \item Either Siggi is not a cabal, or Annie is not a cabal, or neither one of them is a cabal.
  \item If Elizabeth is a cabal, then everyone is a Cabal. So, Elizabeth can not be a cabal, considering the previous item.
  \item If Annie is a cabal then Siggi is a cabal. So Annie is not a Cabal, considering at least one of them is not a cabal.
  \item If either Ben or Albert are cabal, then Tom is not a cabal.
  \item if eight Ben or Siggi are cabal, then Adam is not a cabal.
  \item So, at least three cabal, with the possibilities: Adam, Tom, Albert, Ben, Siggi
  \item Suppose Ben is Cabal, then Tom and Adam are not cabal. The group would be: Ben, Albert, Siggi.
  \item If Tom is cabal, then Albert and Ben are not. The group would have at most two people, since if Siggi is cabal, then Adam is not.
  \item If Adam is cabal, then Siggi and Ben are not.  The group would have at most two people, since if Albert is cabal, then Tom is not.
  \item The only possible group is Ben, Albert, and Siggi.
\end{enumerate}

\end{document}